The SMT Competition 2015--2018

### 2018-09-24 2018/report/SMT-COMP.tex
Minor progress on organization/timeline

>>>>

The SMT Competition is organized under the direction of the SMT
Steering Committee, which appoints the competition chair.  This
appointment should happen ``within 30 days from the end of the current
edition of the SMT workshop''~\cite{smt-bylaws} but in practice has
often happened later.  It is then up to the competition chair to
assemble a team of organizers, and to distribute the work for the next
competition.

Each year, the SMT Workshop includes a block of time to present the
competitors and results of the competition.  The workshop is
affiliated with a different conference each year: with CAV in 2015,
with IJCAR in 2016, again with CAV in 2017, and with FLoC in 2018.
Consequently, its date varies by several weeks.  Competition results
were presented on July~19 in 2015, on July~2 in 2016, on July~23 in
2017, and on July~13 in 2018.

Important deadlines are effectively determined by calculating
backwards from the date of the next SMT Workshop.  The competition's
computational workload should be completed approximately two weeks
before the workshop date, to give participants and other parties a
chance to scrutinize the data for errors, allow partial re-runs of
competition jobs if necessary, and give the organizers time to prepare
the results presentation.  While making all data publicly available
well in advance of the official results presentation may impact the
suspense, it has on several occasions helped to uncover serious
problems with the competition tools or the StarExec framework (see
Section~\ref{sec:starexec}) that could have led to invalid results if
they had gone unnoticed.
\begin{tjark}
  Discuss these issues somewhere, add (forward?) reference here.
\end{tjark}

It takes up to three weeks to run all competition jobs on the StarExec
cluster, so the final submission deadline for solvers needs to be
about five weeks before the workshop date.  The competition imposes a
separate deadline for first versions of solvers about seven weeks
before the workshop date.  This deadline has proved useful for the
organizers to obtain an accurate estimate on the number of competing
solvers, and to run preliminary tests with some of the submitted
solvers to identify potential issues.  Participants can still make
changes to their solver until the final deadline but are encouraged to
use this period for bug-fixing only.

Around the initial solver deadline, the organizers also aim to publish
the latest version of the competition tools, and--in collaboration
with the SMT-LIB maintainers--to release a new version of the SMT
Library.

\begin{tjark}
  WIP

  Also: Call for Comments in February/March\\
  Draft rules in April

  SMT-LIB release dates:\\
  2015-06-01 (vs. 06-01)\\
  2016-05-23 (vs. 05-15)\\
  2017-06-05 (vs. 06-04)\\
  2018-05-20 (vs. 05-27)
\end{tjark}
